Noisy Work: A Review of The Uncertainty Visualisation Literature

### 2024-02-01 paper.qmd
added in taxonomy screenshots from papers
added link to twitter thing tom found

@@

@@

- Hurricane risk is not only the path, but also the storm surge and wind speed. @Spiegelhalter2017
- coloured maps for earthquake risk are easily interpretable @Spiegelhalter2017
# 5 Great Examples
- best things you have seen and why they are the best
- can't have a best practices because you need experimental results and my point is that the experiments aren't testing the right things
- pixel map
  - Similar to what could be good but its computation isnt quite what I would like
  - heaps of sample depictions are animated and that is not always possible, but this is a clear indicator of how you can do a sample visualisaiton
  - hasnt been tested so it is unclear if this actually works at signal supression
- VSUP
  - The purpose of uncertainty is clear in the design and it is signal supression
  - Supression is not the only uncertainty feature we should be interested in (shape is also important which is why I have beef with over smoothing and something visualisation is very good to express) but by being clear in its goal it knows what it is
  - It addresses several key issues with the bivariate map that arrise in general and especially when it is used for visualising uncertainty 
- the census dot map (has been taken down but CNN replicated it [here](https://edition.cnn.com/interactive/2021/us/census-race-ethnicity-map/))
  - I love a good depiction of a sample
  - You can see the sparse regions and the pop 
  - it is similar to the pixel map (could also be singal supression but it is not tested)
  - the sample depiction works well with the interactivity and you can see the signal that is appropriate for a particular level of zoomed in. If you zoom out the points turn into solid colours and show clear signal.
- The new york times class mobility and race animated plot [here](https://www.nytimes.com/interactive/2018/03/19/upshot/race-class-white-and-black-men.html) 
- the animated surface classifications from that satelite images experimental paper
- the climate change scenario uncertainty. There are quite a few of these:
  - [e.g.1](https://earthobservatory.nasa.gov/features/GlobalWarming/page5.php)
  - [e.g.2](https://climatechange.chicago.gov/sites/production/files/2016-07/scenariotempgraph_0.jpg)
  - there are a few examples on the [climate change scenario wiki](https://en.wikipedia.org/wiki/Climate_change_scenario)
  - Good example of uncertainty that has uncertainty from two different sources (human decision in the form of inputs and statistical uncertainty), one of which cant be quantified.
  - a good example in how you can combine two different  types of uncertainty

>>>>

![Example of different uncertainty taxonomies](paperscreenshots/collage1.jpg){#fig-location}

@@

![Example of different uncertainty visualisation taxonomies](paperscreenshots/collage2.jpg){#fig-location}

@@

- Hurricane risk is not only the path, but also the storm surge and wind speed. @Spiegelhalter2017
- coloured maps for earthquake risk are easily interpretable @Spiegelhalter2017
# 5 Great Examples
- best things you have seen and why they are the best
- can't have a best practices because you need experimental results and my point is that the experiments aren't testing the right things
- pixel map
  - Similar to what could be good but its computation isnt quite what I would like
  - heaps of sample depictions are animated and that is not always possible, but this is a clear indicator of how you can do a sample visualisaiton
  - hasnt been tested so it is unclear if this actually works at signal supression
- VSUP
  - The purpose of uncertainty is clear in the design and it is signal supression
  - Supression is not the only uncertainty feature we should be interested in (shape is also important which is why I have beef with over smoothing and something visualisation is very good to express) but by being clear in its goal it knows what it is
  - It addresses several key issues with the bivariate map that arrise in general and especially when it is used for visualising uncertainty 
- the census dot map (has been taken down but CNN replicated it [here](https://edition.cnn.com/interactive/2021/us/census-race-ethnicity-map/))
  - I love a good depiction of a sample
  - You can see the sparse regions and the pop 
  - it is similar to the pixel map (could also be singal supression but it is not tested)
  - the sample depiction works well with the interactivity and you can see the signal that is appropriate for a particular level of zoomed in. If you zoom out the points turn into solid colours and show clear signal.
- The new york times class mobility and race animated plot [here](https://www.nytimes.com/interactive/2018/03/19/upshot/race-class-white-and-black-men.html) 
- the animated surface classifications from that satelite images experimental paper
- the climate change scenario uncertainty. There are quite a few of these:
  - [e.g.1](https://earthobservatory.nasa.gov/features/GlobalWarming/page5.php)
  - [e.g.2](https://climatechange.chicago.gov/sites/production/files/2016-07/scenariotempgraph_0.jpg)
  - there are a few examples on the [climate change scenario wiki](https://en.wikipedia.org/wiki/Climate_change_scenario)
  - Good example of uncertainty that has uncertainty from two different sources (human decision in the form of inputs and statistical uncertainty), one of which cant be quantified.
  - a good example in how you can combine two different  types of uncertainty
  - [This](https://www.esri.com/arcgis-blog/products/arcgis-pro/mapping/graphical-cartograms-in-arcgis-pro/) has some good maps and some bonkers ones
